\chapter{\textcolor{yellow}{Introduction}} \label{ch:Introduction}

The internet is full with recipes, videos and forum posts promising easy ways to forecast future stocks. Articles on medium.com promise to teach the reader the secrets to successfully predicting future stocks with the help of time series, AI and machine learning. On the other side are people who believe in the efficient market hypothesis and laugh about the attempt to ever beat the market. If the efficient market hypothesis is true, all known information is almost immediately priced in and what movement remains is completely unpredictable. On the other hand, others regard the mere existence and the size of the finance industry as evidence that some people are indeed better than others in predicting the market. In this report we will try to use statistical analysis to predict movements in stock prices. We are ultimately expecting to fail. If it were so simple to successfully and reliably predict stock prices given only a couple of months time - the world would indeed be a very different place. We are therefore in the following exploring different prediction methods and trading strategies mainly with the aim of learning about their features, possibilities and limitations. In Chapter \ref{ch:data} we will explore the data that forms the basis of our analysis: stock market data, analyst reports and externally provided news sentiment scores. Chapter \ref{ch:predictions_ml} will use a machine learning approach to predict stock movement. In Chapter \ref{ch:ts} we will present and apply various time series models to the stock data. Chapter \ref{ch:strategies} will detail a number of commonly applied trading strategies and compare their effectiveness. Lastly Chanpter \ref{ch:conclusion} will shortly summarize our findings. 





%\section{Outline Nikos / Felix }

%General Idea: 

%1. Predict Stocks using
%• Time Series
%• Machine Learning and Sentiments from Text
%2. Use Predictions to Implement Trading Strategies
%3. Evaluate and Compare to Other Trading Strategies
