\chapter{Implementing Trading Strategies}\label{ch:predictions}


\chapter{Trading Strategies}
intorduction: Idea and Process
We compare different Trading Strategies. With the Goal of Predicting Stocks this is interesting in and of itself. For the purpose of the project it also serves as a baseline to compare our Trading Strategy against. 



\subsection{Mean Reversion Models}
Idea: We compute some mean. Then compare the current value to that mean. We compute a Z-Score --> Decision to buy or sell
Needed: Economic Theory. Something like. Mean fluctuates around some unknown true value

\subsubsection{Cumulative Mean on Actual Values}
Idea: 
Plot: Cumulative Mean vs. Actual Time Series
--> We see that the cumulative mean does not capture the time series well. Trend is always behind the current development, since we have a trend

Plot / Table: Money we make from this trading strategy --> Comparison to Buy and Hold

\subsubsection{Cumulative Mean on FD of Log Values / on returns of stock}
Idea: percentage change from daay to day reverts to a mean. 


\subsubsection{Comparison of 90d and 30d moving averages}
Idea: If 30d averages is above 90d average, then sell. And vice versa

\subsubsection{Mean Reversion Portfolio}
Idea: Look at entire portfolio
Always sell the two best performing and buy the two current worst performing stocks


\subsection{Pairs Trading}



\section{Trading Strategies Based on Our Predictions}



\section{Hybrid Trading Strategies}
Take Mean of different predictions?


